\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-19 paper/main.tex
BibTeX citation key changes from updating cdl.bib

Within the Python~\cite{vanR95} community, external
packages that are published in the most popular
repositories~\cite{pypi, cond15} are associated with version numbers
and tags that enable users to guarantee that they are installing
exactly the same code across different computing environments.
Despite that it is \textit{possible} to manually install the intended
version numbers of every dependency of a Python script or package, manually
tracking down those dependencies can impose a substantial burden on
the user.

@@

Since its initial release, \texttt{davos} has found use in a variety
of applications. In addition to managing computing environments
for multiple ongoing research studies, \texttt{davos} is being used by
both students and instructors in programming and methods courses such as
Storytelling with Data~\cite{Mann21b} (an open course on data science,
visualization, and communication) and Laboratory in Psychological
Science~\cite{Mann22} (an open course on experimental and statistical
methods for psychology research) to simplify distributing lessons and
submitting assignments, as well as in online demos such as
\texttt{abstract2paper}~\cite{Mann21a} (an example application of
GPT-Neo~\cite{GaoEtal20, BlacEtal21}) to share ready-to-run code that
installs dependencies automatically.

>>>>

Within the Python~\cite{vanR95} community, external
packages that are published in the most popular
repositories~\cite{Pyth03, cond15} are associated with version numbers
and tags that enable users to guarantee that they are installing
exactly the same code across different computing environments.
Despite that it is \textit{possible} to manually install the intended
version numbers of every dependency of a Python script or package, manually
tracking down those dependencies can impose a substantial burden on
the user.

@@

Since its initial release, \texttt{davos} has found use in a variety
of applications. In addition to managing computing environments
for multiple ongoing research studies, \texttt{davos} is being used by
both students and instructors in programming and methods courses such as
Storytelling with Data~\cite{Mann21d} (an open course on data science,
visualization, and communication) and Laboratory in Psychological
Science~\cite{Mann22} (an open course on experimental and statistical
methods for psychology research) to simplify distributing lessons and
submitting assignments, as well as in online demos such as
\texttt{abstract2paper}~\cite{Mann21e} (an example application of
GPT-Neo~\cite{GaoEtal20, BlacEtal21}) to share ready-to-run code that
installs dependencies automatically.
